Analysis of the Anomalous Doppler Effect from Quantum Theory to Classical Dynamics Simulations

### 2025-05-11 paper modification/CPB-tex-template/CPB Template-LaTeX/paper_v2.tex
review

Integrate \eqref{eq:25}, we have
\begin{equation}
\frac{1}{2}\,m_{\varrho}\left(v_{1}-\frac{\omega}{k}\right)^{2}+\frac{1}{2}\,m_{\varrho}v_{\perp}^{2}=C_{0}
\label{eq:26}
\end{equation}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{Figure8.eps}% Here is how to import EPS art
\caption{\label{fig:8}The trajectory curve of $ (v_\parallel,v_\perp)$.}
\end{figure}
Here $C_{0}$ refers to the initial value. The change in velocity is constrained to a circular trajectory, as shown in Fig.~\ref{fig:8}. At the normal Doppler resonance (NDR), where $v_{1}=\frac{\omega-\omega_{ce}}{k}$, an increase in $v_{1}$ corresponds to an increase in $v_{\perp}$. In contrast, at the anomalous Doppler resonance (ADR), where $v_{1}=\frac{\omega+\omega_{ce}}{k}$, an increase in $v_{1}$ corresponds to a decrease in $v_{\perp}$.

@@

\begin{equation}
\frac{\Delta U}{\Delta T}=\frac{v_{\perp}d\,v_{\perp}}{v_{1}d\,v_{1}}
\label{eq:27}
\end{equation}

@@

\begin{equation}
\frac{d\,v_{\perp}}{d\,v_{1}}=-\,\frac{v_{1}-\frac{\omega}{k}}{v_{\perp}}
\label{eq:28}
\end{equation}

@@

\begin{equation}
\frac{\Delta U}{\Delta T}=-\,\frac{v_{1}-\frac{\omega}{k}}{v_{1}}
\label{eq:29}
\end{equation}

According to the resonant condition $\omega=k\,v_{1}+m\,\omega_{ce}$, substituting $v_{1}$ with $\omega$ and $k$ in \eqref{eq:29}, we obtain:

\begin{equation}
\frac{\Delta U}{\Delta T}=\frac{m\,\omega_{ce}}{k\,v_{1}}
\label{eq:30}
\end{equation}

which agrees with the quantum result as \eqref{eq:13}.

>>>>

Integrate \eqref{eq:25}, we have
\begin{equation}
\frac{1}{2}\,m_{\varrho}\left(v_{1}-\frac{\omega}{k}\right)^{2}+\frac{1}{2}\,m_{\varrho}v_{\perp}^{2}=C_{0}
\label{eq:26}
\end{equation}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{Figure8.eps}% Here is how to import EPS art
\caption{\label{fig:8}The trajectory curve of $ (v_\parallel,v_\perp)$.}
\end{figure}
Here $C_{0}$ refers to the initial value. The change in velocity is constrained to a circular trajectory, as shown in Fig.~\ref{fig:8}. At the normal Doppler resonance (NDR), where $v_{1}=\frac{\omega-\omega_{ce}}{k}$, an increase in $v_{1}$ corresponds to an increase in $v_{\perp}$. In contrast, at the anomalous Doppler resonance (ADR), where $v_{||}=\frac{\omega+\omega_{ce}}{k}$, an increase in $v_{||}$ corresponds to a decrease in $v_{\perp}$.

@@

\begin{equation}
\frac{\Delta U}{\Delta T}=\frac{v_{\perp}d\,v_{\perp}}{v_{||}d\,v_{||}}
\label{eq:27}
\end{equation}

@@

\begin{equation}
\frac{d\,v_{\perp}}{d\,v_{||}}=-\,\frac{v_{||}-\frac{\omega}{k}}{v_{\perp}}
\label{eq:28}
\end{equation}

@@

\begin{equation}
\frac{\Delta U}{\Delta T}=-\,\frac{v_{||}-\frac{\omega}{k}}{v_{||}}
\label{eq:29}
\end{equation}

According to the resonant condition $\omega=k\,v_{||}+m\,\omega_{ce}$, substituting $v_{||}$ with $\omega$ and $k$ in \eqref{eq:29}, we obtain:

\begin{equation}
\frac{\Delta U}{\Delta T}=\frac{m\,\omega_{ce}}{kv_{||}}
\label{eq:30}
\end{equation}

which agrees with the quantum result as Eq.~ref{eq:DU21DT21}.
